The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-05-16 paper.tex
About to address referee comments and other comments

\noindent
We stacked all 300s exposures for each galaxy which pass the seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
To account for this, a polynomial function is fit, using the python package {\tt LMFIT} \citep{Newville2014}, which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn. \\

@@

\noindent
Each 0.1$^{\prime\prime}$ spaxel across a datacube was considered in turn.
The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, was used to determine the central wavelength of the redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$. 
We searched a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extracted a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
This truncated spectrum was then used in the fitting procedure for each spaxel.
The width of the extraction region was large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky-line residuals.
A single gaussian model was fit to the extraction region, again using {\tt LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
These parameters, along with the estimate of the noise in the datacube, were used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not.

@@

\begin{enumerate}[label=(\roman*),align=left]
\item The uncertainties on any of the parameters of the gaussian-fit as returned by {\tt LMFIT} must not exceed 30\%
\item $\frac{S}{N_{m}} > 3$
\end{enumerate}

@@

\noindent
Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
High-redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Simons2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation. \\

@@

MC and OJT acknowledge the KMOS team and all the personnel of the European Southern Observatory Very Large Telescope for outstanding support during the KMOS GTO observations.
CMH, AMS and RMS acknowledge the Science and Technology Facilities Council through grant code ST/L00075X/1.
RJM acknowledges the support of the European Research Council via the award of a Consolidator Grant (PI: McLure).
JSD acknowledges the support of the European Research Council via the award of an Advanced Grant (PI J. Dunlop), and the contribution of the EC FP7 SPACE project ASTRODEEP (Ref.No: 312725).
AMS acknowledges the Leverhulme Foundation.
JM acknowledges the support of a Huygens PhD fellowship from Leiden University. DS acknowledges financial support from the Netherlands Organization for Scientific research (NWO) through a Veni fellowship and from FCT through an FCT Investigator Starting Grant and Start-up Grant (IF/01154/2012/CP0189/CT0010).
This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
This work is based on observations taken by the 3D-{\em HST} Treasury Program (GO 12177 and 12328) with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
Based on data obtained with the European Southern Observatory Very Large Telescope, Paranal, Chile, under Large Program 185.A-0791, and made available by the VUDS team at the CESAM data center, Laboratoire d'Astrophysique de Marseille, France.

>>>>

\noindent
We stacked all 300s exposures for each galaxy which pass the seeing criteria using 3-sigma clipping, leaving us with a flux and wavelength-calibrated datacube for every object in the KDS sample.
We have found that the thermal background is often under-subtracted across the spatial extent of the cube following a first pass through the pipeline, leading to excess flux towards the long wavelength end of the {\it K}-band.
To account for this, a polynomial function is fit, using the python package {\scriptsize LMFIT} \citep{Newville2014}, which makes use of the Levenberg-Marquardt algorithm for non-linear curve fitting, to the median stacked spectrum from spaxels in the datacube which contain no object flux and then subtracted from each spaxel in turn. \\

@@

\noindent
Each 0.1$^{\prime\prime}$ spaxel across a datacube was considered in turn.
The redshift value determined from fitting the [O~{\sc III}]$\lambda$5007 line in the integrated galaxy spectrum, $z_{sys}$, was used to determine the central wavelength of the redshifted [O~{\sc III}]$\lambda$5007 line, $\lambda_{obs_{5007}}$. 
We searched a narrow region around $\lambda_{obs_{5007}}$ for the peak flux, assumed to correspond to the ionised gas emission, and extracted a 5$\AA$ region (corresponding to 20 spectral elements) centred on this peak.
This truncated spectrum was then used in the fitting procedure for each spaxel.
The width of the extraction region was large enough to encompass unphysically large velocity shifts, but not so large as to compromise the fitting by potentially encompassing regions of the spectrum plagued by strong sky-line residuals.
A single gaussian model was fit to the extraction region, again using {\scriptsize LMFIT} \citep{Newville2014}, returning the values of the best-fitting flux, $F_{g}$, central wavelength, $\lambda_{g}$, and dispersion, $\sigma_{g}$.
These parameters, along with the estimate of the noise in the datacube, were used to assess whether the fitting of the [O~{\sc III}]$\lambda$5007 line is acceptable or not.

@@

\begin{enumerate}[label=(\roman*),align=left]
\item The uncertainties on any of the parameters of the gaussian-fit as returned by {\scriptsize LMFIT} must not exceed 30\%
\item $\frac{S}{N_{m}} > 3$
\end{enumerate}

@@

\noindent
Studies of the redshift evolution of the stellar mass Tully-Fisher relation do not explain how individual, unperturbed galaxies move around the rotation velocity stellar mass plane with redshift. 
High-redshift galaxy surveys typically do not trace the progenitors of those at lower redshift, as evidenced by the larger observed stellar and baryonic masses \citep[e.g.][]{Cresci2009,Reyes2011,Wisnioski2015,Ubler2017}.
Rather, these studies trace the evolution of the relation itself, the position of which is dictated by the mean properties of typical star-forming galaxies at each redshift slice.
Some authors have reported that as redshift increases, the relation shifts towards lower masses at fixed rotation velocity \citep[e.g.][]{Puech2008,Cresci2009,Puech2010,Straatman2017,Ubler2017}.
However most find that when selecting rotation-dominated galaxies between $0.5 < z < 2$ \citep[e.g.][]{Flores2006,Miller2011,Kassin2012,Miller2012,Vergani2012,Miller2014,Contini2015a,DiTeodoro2016,Pelliccia2017,Molina2017,Harrison2017} the results are consistent with zero evolution of the slope and zero-point of the relation.
At $z\simeq3$ observations are limited and in \cite{Gnerucci2011} an offset of $-$1.29 dex towards lower mass at fixed rotation velocity is claimed, although there is large degree of scatter between the individual galaxies, and the AMAZE Clean sample from \cite{Gnerucci2011} defined in \cref{subsec:AMAZE} is consistent with the $z\simeq0$ relation. \\

@@

OJT acknowledges the financial support of the Science and Technology Facilities Council through a studentship award. 
MC and OJT acknowledge the KMOS team and all the personnel of the European Southern Observatory Very Large Telescope for outstanding support during the KMOS GTO observations.
CMH, AMS and RMS acknowledge the Science and Technology Facilities Council through grant code ST/L00075X/1.
RJM acknowledges the support of the European Research Council via the award of a Consolidator Grant (PI: McLure).
JSD acknowledges the support of the European Research Council via the award of an Advanced Grant (PI J. Dunlop), and the contribution of the EC FP7 SPACE project ASTRODEEP (Ref.No: 312725).
AMS acknowledges the Leverhulme Foundation.
JM acknowledges the support of a Huygens PhD fellowship from Leiden University. DS acknowledges financial support from the Netherlands Organization for Scientific research (NWO) through a Veni fellowship and from FCT through an FCT Investigator Starting Grant and Start-up Grant (IF/01154/2012/CP0189/CT0010).
This work is based on observations taken by the CANDELS Multi-Cycle Treasury Program with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
This work is based on observations taken by the 3D-{\em HST} Treasury Program (GO 12177 and 12328) with the NASA/ESA {\em HST}, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
Based on data obtained with the European Southern Observatory Very Large Telescope, Paranal, Chile, under Large Program 185.A-0791, and made available by the VUDS team at the CESAM data center, Laboratoire d'Astrophysique de Marseille, France.
